The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-13 draft/ms.tex
Summary written

% Other Planets
ZZZ Ask Jason about their criteria. \\ Second, we now also include
robustly detected imaging, microlensing, and timing planets, and our
criteria for a `robust detection' are the following (as set by the
QUACBED):

@@

\end{enumerate}
\item Microlensing planets

\item Timing planets

@@

ZZZ (1) We have a list of criteria for 'robustly detected' imaging planets (on our methodology web page) - do we have similar lists of criteria regarding 'robust detections' for microlensing, timing, and astrometry planets?

No, not really.  As I think we discuss in the last EOD paper (check) we relax some conditions for transiting planets (we don't have to have a measured RV amplitude, for instance).  There have been no astrometric planets.  Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).  In general, we accept microlensing planets that are appear in refereed journals as having unambiguously planetary masses.

ZZZ Figure: some comparison figures of Kepler candidate properties vs. EOD
planet properties, such as mass-period, mass-radius?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:conclusion}

We have had two major updates since \cite{Wright2011}. We included Kepler planet candidates and other planets on exoplanets.org. Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily. We also have added some new fields, removed obsolete fields and revised them as necessary.

>>>>

% Other Planets
Second, we now also include
robustly detected imaging, microlensing, and timing planets, and our
criteria for a `robust detection' are the following (as set by the
QUACBED):

@@

\end{enumerate}
\item Microlensing planets:\\
We accept microlensing planets that appear in refereed journals as having unambiguously planetary masses (planet host mass ratio, $q<0.024$). In case of ambiguity, we consult with QUACBED.

\item Timing planets:\\
 Timing planets must have dynamically stable orbits and, ideally, show multiple complete orbits. 
 ZZZ (see Jackson Norris's paper for a discussion of difficulties with timing planets, also cite recent papers by Rob Wittenmyer).

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:conclusion}
We have had two major updates since \cite{Wright2011}. First, we changed the scope of the EOD. We removed the limit on the type of the host star. We included the planets discovered by various methods (e.g. timing) in the EOD. We also have added some new fields, removed obsolete fields and revised them as necessary.

Second, we included Kepler planet candidates and other planets on exoplanets.org. Although they are not included in the EOD, we reported them on our website to help the users explore them and use them easily.

ZZZ add summary for Onsi's section.
